Mamba vs SOTA for Vision Tasks\\ \thanks{$\dagger$ Equal contributions}

### 2024-04-29 paper/main.tex

\subsection{UL-VM-UNet-v2}
In UL-VM-UNet-v2, the number of parallel branches in the Parallel Vision Mamba (PVM) block was increased from 4 to 8. This modification directly decreases the parameter count, further proving the idea proposed in the UltraLight VM-UNet paper \cite{wu2024ultralight} that processing features in parallel with reduced channel counts can significantly reduce parameters while maintaining performance. The channel list is the same as Ultra LightM-UNet's, [8,16,24,32,48,64].

>>>>

\subsection{UL-VM-UNet-v2}
In UL-VM-UNet-v2, the number of parallel branches in the Parallel Vision Mamba (PVM) block was increased from 4 to 8. This modification directly decreases the parameter count, further proving the idea proposed in the UltraLight VM-UNet paper \cite{ultralightvmunet} that processing features in parallel with reduced channel counts can significantly reduce parameters while maintaining performance. The channel list is the same as Ultra LightM-UNet's, [8,16,24,32,48,64].
